---
title: "Model Fits"
author: "Tristan Mahr"
date: "April 28, 2015"
output:
  html_document:
    css: assets/custom.css
  word_document:
    pandoc_args:
    - --reference-docx
    - assets/template.docx
csl: assets/apa.csl
bibliography: assets/lme4.bib
---

```{r  knitr configuration, warning = FALSE, collapse = TRUE}
# Set working directory to parent folder
library("knitr")
opts_knit$set(root.dir = "../")
opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  message = FALSE,
  fig.width = 6.5,
  fig.height = 4.5)
```

```{r}
library("magrittr")
library("knitr")
library("dplyr", warn.conflicts = FALSE)
library("broom")
library("lme4")
library("stringr")
source("R/utils/pretty_printing.R")
# Make a data-frame with AIC, BIC, LL, fixed effects dfs
make_fit_table <- function(model) {
  fits <- model %>%
    glance %>%
    select(-sigma, -deviance, -df.residual) %>%
    round %>%
    mutate(dfs = get_dfs(model))
  fits
}

# Get the fixed effects degrees of freedom
get_dfs <- . %>% logLik %>% attr("df")
```


```{r}
base_dir <- "data/study1/modelling/without_bad_trials/"
```


```{r Experiment 1 models}
lapply(list.files(base_dir, ".Rdata", full.names = TRUE), load, .GlobalEnv)
names(e1_a1)
base_models <- e1_a1 %>% extract(c("gcm_base", "gcm_EVT", "gcm_Age", "gcm_EVTAge"))
gcm_target <- s1_a2 %>% extract("gcm_target")

phon_head_to_head <- e1_phon_unre %>%
  extract(c("gcm_Target_v_Phonological", "gcm_Target_v_Unrelated"))

phon_head_to_head_evt <- e1_phon_unre %>%
  extract(c("gcm_Target_v_Phonological_EVT", "gcm_Target_v_Unrelated_EVT"))

semy_head_to_head <- e1_semy_unre %>%
  extract(c("gcm_Target_v_Semantic", "gcm_Target_v_Unrelated2"))

semy_head_to_head_evt <- e1_semy_unre %>%
  extract(c("gcm_Target_v_Semantic_EVT", "gcm_Target_v_Unrelated2_EVT"))

e1_models <- c(base_models, gcm_target, phon_head_to_head, semy_head_to_head, phon_head_to_head_evt, semy_head_to_head_evt)

# Model names go here
e1_model_names <- c(
  "Base Model",
  "Base With EVT",
  "Base With Age",
  "Base With Age*EVT",
  "Target- vs. Distractor-Initial",
  "(1) Target vs. Phonological",
  "(1) Target vs. Unrelated",
  "(2) Target vs. Semantic",
  "(2) Target vs. Unrelated",
  "(3) Target vs. Phonological With EVT",
  "(3) Target vs. Unrelated With EVT",
  "(4) Target vs. Semantic With EVT",
  "(4) Target vs. Unrelated With EVT"
)
```



```{r Experiment 2 models, eval=TRUE}
list.files("data/study2/modelling")
lapply(list.files("data/study2/modelling", ".Rdata", full.names = TRUE), 
       load, .GlobalEnv)

s2_base_models <- s2_a1[names(s2_a1) != "data"]
s2_gcm_target <- s2_a2 %>% extract("gcm_target")

s2_phon_head_to_head <- s2_phon_unre %>%
  extract(c("gcm_Target_v_Phonological", "gcm_Target_v_Unrelated"))

s2_semy_head_to_head <- s2_semy_unre %>%
  extract(c("gcm_Target_v_Semantic", "gcm_Target_v_Unrelated2"))


s2_phon_head_to_head_evt <- s2_phon_unre %>%
  extract(c("gcm_Target_v_Phonological_EVT", "gcm_Target_v_Unrelated_EVT"))

names(s2_semy_unre)
s2_semy_head_to_head_evt <- s2_semy_unre %>%
  extract(c("gcm_Target_v_Semantic_EVT_no_ranef_cov", "gcm_Target_v_Unrelated2_EVT_no_ranef_cov"))



s2_models <- c(s2_base_models, s2_gcm_target, s2_phon_head_to_head, s2_semy_head_to_head, s2_phon_head_to_head_evt, s2_semy_head_to_head_evt)

# Model names go here
s2_model_names <- c(
  "Dialect Comparison",
  "Base Model",
  "Base With EVT",
  "Base With Age",
  "Base With Age x EVT",
  "Base With Age x EVT x Mat. Ed.",
  "Target- vs. Distractor-Initial",
  "(1) Target vs. Phonological",
  "(1) Target vs. Unrelated",
  "(2) Target vs. Semantic",
  "(2) Target vs. Unrelated",
  "(3) Target vs. Phonological With EVT",
  "(3) Target vs. Unrelated With EVT",
  "(4) Target vs. Semantic With EVT",
  "(4) Target vs. Unrelated With EVT"
)

```










## Appendix B: Model Fits and Formulas

Numerous growth curve analyses were performed on both experiments. Further, the
fixed-effect and random-effect specifications changed from model to model. The
`lme4` package's formula syntax provides a succinct way to describe the
grouping factors used in a mixed-effects model [@Bates2014, pp. 5-6]. The
following tables summarize the measures of model fit and the `lme4` formulas
used for the primary growth curve analyses presented in this artcle. All models
were fit with maximum likelihood. The head-to-head comparison models, indicated
with paired numbers in the tables, were fit with generalized linear models with
a logit link function.


### Experiment 1

```{r, echo = FALSE}
models <- e1_models
model_names <- e1_model_names
```

```{r Model Fits, echo = FALSE}
analysis_table <- lapply(models, make_fit_table) %>%
  bind_rows %>%
  mutate(Model = model_names) %>%
  select(Model, dfs, AIC, BIC, logLik) %>%
  rename(`df (Fixed Effects)` = dfs, `Log-Likelihood` = logLik)

kable(analysis_table, format = "pandoc", caption = "Measures of model fit")
```


```{r Model Formulas, echo = FALSE}
formulas <- models %>%
  lapply(get_formula_literal) %>%
  lapply(rewrite_formula) %>%
  unlist

data_frame(Model = model_names, `lme4 Formula` = formulas) %>%
  kable(format = "pandoc", caption = "Model specifications")
```

### Experiment 2

```{r, echo = FALSE, eval=TRUE}
models <- s2_models
model_names <- s2_model_names
```

```{r, ref.label="Model Fits", echo = FALSE, eval=TRUE}

```

```{r, ref.label="Model Formulas", echo = FALSE, eval=TRUE}

```


### References
