---
output:
  html_document:
    css:
    - assets/custom.css
  word_document:
  - default
---

# Tables

This script generates tables for use in the manuscript.


```{r knitr configuration, warning = FALSE, echo = FALSE}
# Set working directory to parent folder
library("knitr")
opts_knit$set(root.dir = "../")
opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.width = 6.5,
  fig.height = 4.5)
```



```{r, warning = FALSE, message = FALSE}
### Libraries and data-cleaning helpers
library("stringr")
library("tidyr")
library("dplyr")
library("magrittr")
options(stringsAsFactors = FALSE, digits = 4)

n_missing <- . %>% is.na %>% sum

# Clean up medu values, abbreviate
normalize_medu <- function(xs) {
  xs <- ifelse(xs == "4 year college degree", "College", xs)
  xs <- ifelse(xs == "", "Declined", xs)
  substr(xs, 1, 4)
}

# First pass at cleaning data
normalize_values <- . %>% 
  mutate(
    # Don't numerically code variables
    AAE = ifelse(AAE, "AAE", "MAE"),
    Sex = ifelse(female, "F", "M"),
    # Abbreviate medu to 3-4 characters
    medu = normalize_medu(medu))

# how many scores are missing (for footnotes)
count_missings <- . %>% group_by(medu_lmh) %>% 
  summarise(
    evts_raw_missing = n_missing(EVT_Raw),
    evts_std_missing = n_missing(EVT_Standard),
    ppvts_raw_missing = n_missing(PPVT_Raw),
    ppvts_std_missing = n_missing(PPVT_Standard))

# Look-up list for abbreviated medu values
medu_codes <- c(
  Less = "low", 
  GED  = "low",
  High = "low",
  Some = "mid",
  Tech = "mid",
  Trad = "mid",
  # Use "top" so alphabetical order matches lmh order 
  Coll = "top",
  Grad = "top",
  Decl = "decl")
```


```{r}
### Functions for formatting/display

parenthesize <- . %>% sprintf("(%s)", .)

capitalize <- function(xs) {
  substr(xs, 1, 1) <- xs %>% substr(1, 1) %>% toupper
  xs
}

# mean (sd)
mean_sd <- function(xs) { 
  avg <- xs %>% mean(na.rm = TRUE) %>% round(2)
  sds <- xs %>% sd(na.rm = TRUE) %>% round(2)
  paste(avg, parenthesize(sds))
}

# n. AAE / n. SAE
report_dialect <- function(xs) {
  AAEs <- sum(xs == "AAE")
  SAEs <- sum(xs == "MAE")
  paste0(AAEs, "/", SAEs)
}

# n. total (n. boys)
report_n_w_boys <- function(xs) {
  n <- length(xs)
  boys <- sum(xs == 0)
  paste(n, parenthesize(boys))
}

# replace "top" with "high"
top_to_high <- . %>% str_replace("top", "high") %>% 
  str_replace("mid", "middle") %>% 
  str_replace("decl", "declined")


count_medus <- function(xs) {
  breakdown <- xs %>% table %>% as.list
  names(breakdown) <- names(breakdown) %>% top_to_high
  breakdown
}

# Create equations
list_to_eq <- . %>% sprintf("%s&nbsp;=&nbsp;%s", names(.), .)

```


```{r}
### Load data

d1 <- read.csv("data/study1/01_test_scores.csv") %>% as.tbl %>% normalize_values 
d2 <- read.csv("data/raw/scores/s2_matches.csv") %>% as.tbl %>% normalize_values

# Recode medu values into three levels
d1$medu_lmh <- medu_codes[d1$medu]
d2$medu_lmh <- medu_codes[d2$medu]

# Clean up col names from study one
names(d1) <- names(d1) %>% str_replace("_raw", "_Raw") %>% 
  str_replace("_standard", "_Standard")
```

## Table 1

```{r, results = 'asis'}
table_1 <- d1 %>% 
  summarise(
    n = report_n_w_boys(female),
    ages = mean_sd(Age),
    evt = mean_sd(EVT_Standard),
    ppvt = mean_sd(PPVT_Standard))

table_1$medu <- d1$medu_lmh %>% 
  count_medus %>% 
  list_to_eq %>% 
  paste0(collapse = "; ")

col_names_1 <- c(
  "N participants (N boys)", 
  "Mean (SD) age in months", 
  "Mean (SD) EVT-2 standard score", 
  "Mean (SD) PPVT-4 standard score^1^",
  "N at each maternal education level^2^" 
)

d1_missings <- count_missings(d1) 
```

Table 1. Demographic information and EVT-2/PPVT-4 standard scores for participants in Experiment 1.

```{r, results = 'asis', echo = FALSE}
table_1 %>% kable(col.names = col_names_1)
```

^1^PPVT-4 scores are missing for `r d1_missings[[3, "ppvts_std_missing"]]` child from a high maternal education level family.

^2^Declined = family chose not to provide maternal education level; High = college or graduate degree; Middle = some college, associate’s degree, or technical school degree; Low = high school diploma, GED, or less than high school diploma.



## Table 2

```{r, results = 'asis'}
table_2 <- d2 %>% 
  group_by(medu_lmh) %>% 
  summarise(
    n = report_n_w_boys(female),
    ages = mean_sd(Age),
    dialect = report_dialect(AAE),
    evt = mean_sd(EVT_Standard),
    ppvt = mean_sd(PPVT_Standard)) %>% 
  mutate(medu_lmh = medu_lmh %>% top_to_high %>% capitalize)

col_names <- c(
  "Maternal education level^1^", 
  "N participants (N boys)", 
  "Mean (SD) age in months", 
  "AAE/MAE speakers", 
  "Mean (SD) EVT-2 standard score", 
  "Mean (SD) PPVT-4 standard score^2^"
)

d2_missings <- count_missings(d2) 
```

Table 2. Demographic information and EVT-2/PPVT-4 standard score for participants in Experiment 2.

```{r, echo = FALSE, results='asis'}
table_2 %>% kable(col.names = col_names, format = "pandoc")
```

^1^High = college or graduate degree; Middle = some college, associate’s degree, or technical school degree; Low = high school diploma, GED, or less than high school diploma.

^2^PPVT-4 scores are missing for `r d2_missings[[2, "ppvts_std_missing"]]` children from middle maternal education level families, and `r d2_missings[[1, "ppvts_std_missing"]]` children from low maternal education level families.


## Missing scores

### S1

```{r, reslts = 'asis'}
d1_missings %>% kable
```

### S2

```{r, results = "asis"}
d2_missings %>% kable
```

